SIR Model With Testing Flows and Isolation

### 2020-11-05 codes/ali_test_sir.Rmd
sim when W_s=W_I

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=.8,gamma=1/3, omega=0.25, rho=0.01, 
             W_S=0.5, W_I=1, W_R=1, #weights
             p_S=0, p_I=1, p_R=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2 #eta_w/eta_t
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
# Conditional stop for desolver
# rootfun <- function (time, state,params) { 
#   unpack(as.list(c(state,params)))
#   return(I_u - 1) }
```

@@

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
n_out <- 5 ## facets (rows/cols)
n_in <- 41 ## grid N within facets
 # specify the ranges
 beta  <- 0.5  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=n_out)
 eta_t <- seq(0,1, length.out=n_out) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.011,1 , length.out=n_in) #note omega must be > rho, was 0.1

@@

```{r contour_R0_2, message=FALSE,warning=FALSE }
 # specify the ranges
eta_t <- seq(0.001,0.5, length.out=n_out)  
s <- seq(1,2,length.out=n_out)

>>>>

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=.8,gamma=1/3, omega=0.25, rho=0.01, 
             W_S=1, W_I=1, W_R=1, #weights
             p_S=0, p_I=1, p_R=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2 #eta_w/eta_t
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
# Conditional stop for desolver
# rootfun <- function (time, state,params) { 
#   unpack(as.list(c(state,params)))
#   return(I_u - 1) }
```

@@

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
n_out <- 5 ## facets (rows/cols)
n_in <- 41 ## grid N within facets
 # specify the ranges
 beta  <- 0.4  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=n_out)
 eta_t <- seq(0,1, length.out=n_out) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, was 0.011

@@

```{r contour_R0_2, message=FALSE,warning=FALSE }
 # specify the ranges
beta  <- 0.35  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=n_out)
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.1,1.5 , length.out=n_in) #note omega must be > rho, was 0.011

eta_t <- seq(0.001,0.01, length.out=n_out)  
s <- seq(1,2,length.out=n_out)
